---
title: "Crime Reports Notes"
author: "Nathan Hattersley"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(kableExtra)
crime <- vroom("data/crime_reports.csv.gz")
```

Rather than pick out individual offense codes, I noticed that there is a category description variable:

```{r}
crime %>% distinct(category_description) %>% kbl %>% kable_styling
```

It seems like theft and robbery are the offense categories that we would care about. Let's look at the unique offenses listed in those categories:

```{r}
crime %>% 
  dplyr::filter(category_description %in% c("Robbery", "Theft")) %>% 
  count(highest_offense_description, highest_offense_code) %>% 
  kbl() %>%
  kable_styling()
```

I think that two that don't belong are "BREACH OF COMPUTER SECURITY" and "MISAPPLY FIDUCIARY PROP" (what homeless are fiduciaries?)

How much data will we have to geocode?

```{r}
date_range <- ymd(20150101) %--% ymd(20191231)
relevant_crime <- crime %>%
  dplyr::filter(category_description %in% c("Robbery", "Theft")) %>%
  dplyr::filter(!highest_offense_code %in% c(1109, 1201)) %>%
  dplyr::filter(occurred_date_time %within% date_range)

relevant_crime %>% count(is.na(latitude) | is.na(longitude))
```

Yes! So the latitude and longitude are well specified for the vast marjority of these cases. 
